Sketch Recognition and Understanding

### 2009-04-27 trunk/draft/chapterSurvey.tex

@@

 \subsection*{Optimization Algorithms}
 In optimization problems, the algorithms attempts to find a feasable solution which satisfy all constrain of this problem. An optimal solution is the best feasable solution in the solution space. PSO is a population based stochastic search algorithm\cite{PSOFirst,PSO2}. It models the  % which has the best or  select a set of paramters that satisfy all constrains 
 The Particle Swarm Algorithm is an adaptive algorithm
based on a social-psychological metaphor [1]. A
population of individuals adapt by returning stochastically
toward previously successful regions in the search
space, and are influenced by the successes of their topological
neighbors. Most particle swarms are based on two
sociometric principles. Particles fly through the solution
space and are influenced by both the best particle in the
particle population and the best solution that a current
particle has discovered so far. The best particle in the
population is typically denoted by (global best), while the
best position that has been visited by the current particle
is denoted by (local best). The (global best) individual
conceptually connects all members of the population to
one another. That is, each particle is influenced by the
very best performance of any member in the entire population.
The (local best) individual is conceptually seen
as the ability for particles to remember past personal
successes.

@@

>>>>

The underliny research in swarm intelligence led to optimization algorithm that simulate the animal social behvaiors. 
Ant Colony Optimization (ACO) algoirithm simulate how ants search for optimize path for food \cite{}.  Real ants leave evidence of their exploriation while they are searching for food. This trail is used by other ants to locate shortest distance between the colony and food location. ACO use similar type of cooperation between agents to find optimal solution.  The synchronous bird flock movement was simulated in \cite{PSOFirst,PSO2}.  Kennedy and Eberhart \cite{PSOFirst,PSO2} simulated the rules of bird flock movement and introduced the Particle Swarm Optimization Algorithm (PSO).

% Kennedy and Eberhart \cite{PSOFirst,PSO2} introduced Particle Swarm Optimization Algorithm (PSO). The algorithm simulate the moving

@@

 \subsection*{Optimization Algorithms}
 In optimization problems, the algorithms attempts to find a feasable solution which satisfy all constrain of this problem. An optimal solution is the best feasable solution in the solution space. PSO is a population based stochastic search algorithm\cite{PSOFirst,PSO2}. It simulate the  % which has the best or  select a set of paramters that satisfy all constrains

 Studies to simulate the underly
ing rules of bird social behavior led to a new approach for optimizing realvalued
functions 	Particle Swarm Optimization PSO Kennedy and Eberhart 

 This new approach combines notions of evolutionary computation and
swarm theory Kennedy 

PSO provides a populationbased search procedure where each individual is
abstracted as a 	particle that 
ies around in a multidimensional search space
The best positions encountered by a particle and its neighbor determine the parti
cles trajectory along with other PSO parameters In other words a PSO system
attempts to balance exploration and exploitation by combining local and global
search methods

 The Particle Swarm Algorithm is an adaptive algorithm
based on a social-psychological metaphor [1]. A
population of individuals adapt by returning stochastically
toward previously successful regions in the search
space, and are influenced by the successes of their topological
neighbors. Most particle swarms are based on two
sociometric principles. Particles fly through the solution
space and are influenced by both the best particle in the
particle population and the best solution that a current
particle has discovered so far. The best particle in the
population is typically denoted by (global best), while the
best position that has been visited by the current particle
is denoted by (local best). The (global best) individual
conceptually connects all members of the population to
one another. That is, each particle is influenced by the
very best performance of any member in the entire population.
The (local best) individual is conceptually seen
as the ability for particles to remember past personal
successes.

@@

\subsection*{Advantages}
Particle swarm Optimization is gar
